%% 
%% Copyright 2019-2020 Elsevier Ltd
%% 
%% This file is part of the 'CAS Bundle'.
%% --------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%%
%% Template article for documentclass for 
%% double column output.

%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-sc}

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
% for EPS, load graphicx instead
\usepackage{graphics}
\usepackage{graphicx}
% for umlauts and other diaeresis
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{enumitem}
\usepackage{epstopdf}
\usepackage{multicol}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{hyperref}

\hypersetup{
colorlinks=true,
linkcolor=black,
filecolor=black,
urlcolor=black,
citecolor=black,
menucolor=black,
}

\graphicspath{{images/}}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{BreastScreening-AI}
\shortauthors{Calisto et~al.}
\setlength{\marginparwidth }{2cm}

\title{Introduction of Human-Centric AI Assistant to Aid Radiologists for Multimodal Breast Image Classification}

\author[1]{Francisco Maria Calisto}[orcid=0000-0001-8179-7872]
\ead{francisco.calisto@tecnico.ulisboa.pt}
%\ead[URL]{https://web.tecnico.ulisboa.pt/francisco.calisto}

\author[1]{Carlos Santiago}[orcid=0000-0002-4737-0020]
%\ead{carlos.santiago@tecnico.ulisboa.pt}
%\ead[URL]{https://welcome.isr.tecnico.ulisboa.pt/author/carlosjorgemariz}

\author[2]{Nuno Nunes}[orcid=0000-0002-2498-0643]
%\ead{nunojnunes@tecnico.ulisboa.pt}
%\ead[URL]{https://fenix.tecnico.ulisboa.pt/homepage/ist132720}

\author[1]{Jacinto C. Nascimento}[orcid=0000-0001-7468-5127]
%\ead{jan@isr.tecnico.ulisboa.pt}
%\ead[URL]{http://users.isr.tecnico.ulisboa.pt/~jan}

\address[1]{Institute for Systems and Robotics, Avenida Rovisco Pais 1, 1049-001, Lisbon, Portugal}
\address[2]{Interactive Technologies Institute, Caminho da Penteada, 9020-105, Funchal, Madeira, Portugal}

\begin{abstract}
In this research, we take an HCI perspective on the opportunities provided by {\it AI techniques} in medical imaging, focusing on workflow efficiency and quality, preventing errors and variability of diagnosis in Breast Cancer. Starting from a holistic understanding of the clinical context, we developed {\it BreastScreening} to support {\it Multimodality} and integrate {\it AI techniques} (using a deep neural network to support automatic and reliable classification) in the medical diagnosis workflow.
This was assessed by using a significant number of clinical settings and radiologists.
Here we present:
i) user study findings of 45 physicians comprising nine clinical institutions;
ii) list of design recommendations for visualization to support breast screening {\it radiomics};
iii) evaluation results of a proof-of-concept {\it BreastScreening} prototype for two conditions {\it Current} (without AI assistant) and {\it AI-Assisted}; and
iv) evidence from the impact of a {\it Multimodality} and {\it AI-Assisted} strategy in diagnosing and severity classification of lesions.
The above strategies will allow us to conclude about the {\it behaviour} of clinicians when an AI module is present in a diagnostic system.
This {\it behaviour} will have a direct impact in the clinicians workflow that is thoroughly addressed herein.
Our results show a high level of acceptance of {\it AI techniques} from radiologists and point to a significant reduction of cognitive workload and improvement in diagnosis execution.
\end{abstract}

\begin{keywords}

Human-Computer Interaction

Artificial Intelligence

Healthcare

Medical Imaging

Breast Cancer

\end{keywords}

\maketitle

\input{body}

%\appendix
%\section{Appendix}

\printcredits

\clearpage

%% Loading bibliography style file
\bibliographystyle{cas-model2-names}

% Loading bibliography database
\bibliography{bibliography}

\clearpage

% ----------------------------------------------------------------------
% HERE GO THE APPENDIXES IF REQUIRED
% If not required just comment the blocks
\appendix
%% First Appendix
\pdfpageheight=\pagetotal
\pdfbookmark[1]{Appendix}{appendix}
\input{appendixes/app001.tex}
%% If Printing on DOUBLE SIDED pages, the second page should be white.
%% Otherwise, comment the following command:
% ----------------------------------------------------------------------

\end{document}